%!TEX root =  main.tex
\chapter*{Acknowledgements}
\pagenumbering{gobble}
%\pagestyle{empty}
First of all, I would like to express my sincere gratitude to my mentor professor Goran Sladi\'c, for his unselfish help during the process of writing this thesis and related papers.

My research would have been impossible without the aid and support of colleagues Ivan Proki\'c and Jovana Dedei\'c from Chair of Mathematics. Together we managed to finish our research and publish our first paper to the journal, and we were invited to present our research to eminent colleagues from the \textbf{Imperial College in London}. Before working with them, I had a different view of what research is, and now my view is changed for the better. I hope that we will continue to collaborate in the future, publishing more great papers, and working on interesting and challenging projects and ideas. I would also like to thank members of the committee for their helpful suggestions to make this thesis better.

I am profoundly grateful to Dejan Miji\'c, who first introduced me to formal models, and their importance in the research area of the distributed systems. Before our talks, I had no idea how to actually test, and prove my work. I would blindly try all scenarios that come to my mind, and ultimately prove probably nothing.

I would like to thank all my friends, relatives and other people who showed me how (not) to act, and how to be a better person. To my university professors, teaching assistants and colleagues from Chair of Informatics, and Chair of Applied Computer Science who pushed me to reach my full potential, to evolve, and ultimately finish my PhD. I would like to express my gratitude to Biljana Duda\v s for all the good deeds she has done over the years, Nata\v sa Petrovi\'c and Vanja Bogi\'cevi\'c for doing proofreading of this thesis. 

Special thanks for my \emph{MetaDoktor} teammates Vladimir Ivan\v cevi\'c, Marko Kne\v zevi\'c from Faculty of Technial Sciences and Danica Mandi\'c from Faculty of Medicine, our collaboration sparked my interest for doing serious research. I have learned so much from you all, and enjoyed the time we spent working on \emph{Dr Warehouse} project were we ultimately won \textbf{best paper award}.

In the end, I would like to dedicate this work to my grandparents, answering their most interesting question --- I have finished school finally (Unless I decide to pursue post-doc)! The journey was hard, and not so pleasant most of the time, I had much more those who congratulate, than those who support. But, \emph{"if I have seen further it is by standing on the shoulders of Giants."}\footnote{Sir Isaac Newton letter to Robert Hooke, 1675}.