%!TEX root =  main.tex
\chapter*{List of publications}
\pagenumbering{gobble}
%
This thesis is the result of years of research and development, and it is based on the previously presented papers at conferences in journals.

\begin{itemize}
	
	\item Journal publications
	
	\begin{enumerate}[start=1,label={(\bfseries \arabic*)}]
		\item MDPI Sensors Placeholder
		\item M. Simić, I. Prokić, J. Dedeić, G. Sladić and B. Milosavljević, "Towards Edge Computing as a Service: Dynamic Formation of the Micro Data-Centers," in IEEE Access, vol. 9, pp. 114468-114484, 2021, doi: 10.1109/ACCESS.2021.3104475.
		\item  Ivančević V., Knežević M., Simić M., Luković I., Mandić D.:  Public Healthcare and Epidemiology with Dr Warehouse, International Journal on Advances in Software, 2013, Vol. 6, No. 3-4, pp. 329-342, ISSN 1942-2628
	\end{enumerate}
	
	\item Conference papers
	
	\begin{enumerate}[start=1,label={(\bfseries \arabic*)}]
		\item Simić, M., Stojkov, M., Sladić, G., Milosavljević, B.  CRDTs as replication strategy in large-scale edge distributed system: An overview. In: Zdravković, M., Konjović, Z., Trajanović, M. (Eds.) ICIST 2020 Proceedings Vol.1, pp.46-50, 2020, ISBN 978-86-85525-24-7.
		\item Simić M., Stojkov M., Sladić G., Milosavljević B., Zarić M.:   On container usability in large-scale edge distributed system, 9. International Conference on Information Science and Technology (ICIST), Kopaonik: Society for Information Systems and Computer Networks, 10-13 March, 2019, pp. 97-101, ISBN pp.97-101, 2019.
		\item Simić M., Stojkov M., Sladić G., Milosavljević B.:  Edge computing system for large-scale distributed sensing systems, 8. International Conference on Information Science and Technology (ICIST), Kopaonik: Society for Information Systems and Computer Networks, 11-14 March, 2018, pp. 36-39, ISBN 978-86-85525-22-3.
		\item Simić M., Sladić G., Milosavljević B.:  A Case Study IoT and Blockchain Powered Healthcare , 8. PSU-UNS International Conference on Engineering and Technology - ICET, Novi Sad: University of Novi Sad, Faculty of Technical Sciences , 8-10 June, 2017, pp. 1-4, ISBN 978-86-7892-934-2.
		\item Simić M.:  Clover: Property Graph based metadata management service, 6. International Conference on Information Science and Technology (ICIST), Kopaonik: Society for Information Systems and Computer Networks, 29-2 February, 2016, pp. 81-85, ISBN 978-86-85525-18-6.
		\item Ivančević V., Knežević M., Simić M., Luković I., Mandić D.:  Public Healthcare and Epidemiology with Dr Warehouse, International Journal on Advances in Software, 2013, Vol. 6, No. 3-4, pp. 329-342, ISSN 1942-2628
	\end{enumerate}
	
\end{itemize}
%
%